Analysing Constraint Grammars with a SAT-solver

### 2016-02-11 paper/lrec/lrec2016_listenmaa_claessen.tex
remove more words
nitpicking
typofixes, minor tweaks
update makefile & add Fran to acknowledgements
use LREC official stylesheet

%
% File nodalida2015.tex
%
% Contact beata.megyesi@lingfil.uu.se
%
% Based on the instruction file for EACL 2014
% which in turn was based on the instruction files for previous 
% ACL and EACL conferences.

\documentclass[11pt]{article}
\usepackage{nodalida2015}
\usepackage{times}
\usepackage{mathptmx}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{cite}
\usepackage{graphicx}
%\usepackage{slantsc}
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{authordate1-4}
\usepackage{multirow}
%\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

\usepackage{fontspec}
\usepackage{wasysym}

\newcommand{\mainfontfamily}{Palatino}
\setmainfont[
  Ligatures=TeX,
  Scale=0.9,
]{\mainfontfamily}

\newfontfamily\scshape[Letters=SmallCaps, Numbers=Uppercase]{Palatino
  Small Caps}

\newcommand{\monofontfamily}{Monaco} % Monaco
\setmonofont[Scale=0.8]{\monofontfamily}

\usepackage{color}
\newcommand{\todo}[1]{{\color{cyan}\textbf{[TODO: }#1\textbf{]}}}

@@

\author{Inari Listenmaa \and Koen Claessen \\
 Chalmers University of Technology, Gothenburg, Sweden \\
 {\tt \{inari,koen\}@chalmers.se} }

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
%\small
We describe a method for
 analysing Constraint Grammars by encoding the
rules in SAT.
Our tools can detect internal conflicts or redundancies in a grammar,
as well as generate examples to demonstrate the effect of some rule or
rule set.
This can help users to diagnose and improve their grammars.
No corpus is required, only a morphological lexicon.
%We test our tools with grammars from 100-1000 rules.
\end{abstract}

@@

\section*{Acknowledgments}
We thank Eckhard Bick for the idea to apply SAT to CG analysis.

\bibliographystyle{acl}
\bibliography{cg}

>>>>

\documentclass[10pt, a4paper]{article}
\usepackage{lrec2016}
\usepackage{multibib}
\newcites{languageresource}{Language Resources}
\usepackage{graphicx} % for eps graphics
\usepackage{epstopdf}
\usepackage[latin1]{inputenc}

% Inari's additions
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{color}
\newcommand{\todo}[1]{{\color{cyan}\textbf{[TODO: }#1\textbf{]}}}
\usepackage{units} % for nicefrac
\usepackage{wasysym} % for clock

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\name{Inari Listenmaa, Koen Claessen}

\address{University of Gothenburg, Chalmers University of Technology \\
         Gothenburg, Sweden \\
         inari@chalmers.se, koen@chalmers.se\\}

\abstract{
We describe a method for analysing Constraint Grammars by encoding the
rules in SAT.
Our tools can detect internal conflicts or redundancies in a grammar,
as well as generate examples to demonstrate the effect of some rule or
rule set.
This can help users to diagnose and improve their grammars.
No corpus is required, only a morphological lexicon. \\ 
\newline 
\Keywords{Constrain Grammar, SAT, Grammar Analysis} }

\begin{document}

\maketitleabstract

@@

\section*{Acknowledgments}
We thank Eckhard Bick for the idea to apply SAT to CG analysis, and Francis Tyers for insightful discussions.

\section{Bibliographical References}
\label{main:ref}

\bibliographystyle{lrec2016}
\bibliography{cg}

% \section{Language Resource References}
% \label{lr:ref}
% \bibliographystylelanguageresource{lrec2016}
% \bibliographylanguageresource{cg}
